Learning to Synthesize Rules for Network Intrusion Detectors

### 2020-01-06 paper/paper.tex
pass on section 4

\Mar{------------------ estou aqui}

First, it produces a
potentially overspecified rule that captures the malicious traffic
provided on input. In this step, \tname\ finds options by
\emph{reverse engineering} the positive traffic. It extracts tokens
from the malicious message and uses them to define the initial
rule. We say that this rule overfits the problem as it satisfies the
success criterion of only capturing the positive traffic, however it
is unlikely that it will be able to generalize to other attacks,
\ie{}, attacks of the same kind, but with different data. The reason
is that many options added to the rule are unimportant for
discriminating the attack. In the second step, \tname{} uses negative
examples to \emph{minimize} the rule, discarding unnecessary
options. Note that any subset of the original set of options captures
the positive traffic. The minimization step uses a population-based
gradient descent-like search to generate minimal solutions.

>>>>

\tname\ works as follows. First, it produces a potentially
overspecified rule that captures the malicious traffic, provided on
input in the form of pcap files~\cite{pcap}. In this step,
\tname\ detects rule options in correspondence with the input messages
(see Section~\ref{sec:rules-and-packets}). It is worth noting that the
rule produced in this step can include more options than the golden
rule (see Section~\ref{sec:suri-metas-coverage}). Consequently, the
use of that rule could lead, in principle, to false negatives as not
all manifestations of the same attack are identical, \ie{}, the
content of messages for two instantiations of a given attack may
differ. Second, \tname{} generates plausible rules similar to the one
produced in the previous step. It is worth noting that any subset of
the original set of options captures the malicious traffic. As the
generation procedure discards options from the initial rule, it
satisfies the invariant of capturing malicious traffic by
construction. However, the goal of \tname\ is to produce rules that
capture \emph{only} malicious traffic. To achieve that goal, \tname{}
uses benign traffic from public databases to check that the
\nids\ instantiated with a given rule does not capture benign
traffic. The minimization step uses a population-based gradient
descent-like search to find all plausible rules, which are derived
from the rule obtained in the previous step. Third,
\Fix{...elaborate...}
